\documentclass[a4paper,12pt]{article}
\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english,russian]{babel}
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathtools}

\begin{document}
Good morning everybody.
Let me start with the question: have you ever had problems with sleep?
Today I’m going to tell you about sleep disorders.\\

Because of the limited time, I’ll cover three areas\\
1. negative influence on health.\\
2. common reasons of disorders.\\
3. recommendations for good sleep.\\

I’ll be happy to answer your questions at the end of my talk.\\

So, let’s look first at negative influence of sleep disorders on health. There are a lot of different sleep disorders that can seriosly damage your health, for example: insomnia and bruxism.
Insomnia is typically followed by daytime sleepiness, low energy, irritability, and a depressed mood. If this disorder lasts much time it hits on health, for example insomnia victim can get mental problems, elevated risk of stroke and overweight problems. Bruxism is tapping or grinding by teeth that can destroy enamel.\\

Let’s turn now to common reasons of this disorders. Most of reasons can be divided on two categories: mental(depression, apathy) and physical such as discomfortable conditions, high temperature and humidity.\\

Finally recommendations for good sleep. If you have any problems with sleep or want to prevent them, you should try to do physical exersizes few hours before going to bed, not to use any gadgets and keep healthy diet.
Okay, that ends my talk.\\

Let me summarise what we've looked at.
Sleep disorder is serious health problem, but if you will follow some simple pieces of advice you can avoid it.
That’s all I have to say.
To sum up, I hope I’ve succeeded in showing you that healthy sleep is an important condition of normal life.

Thank you for your attention.\\

Are there any questions?\\
\end{document}