\documentclass[a4paper,16pt]{article}
\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english,russian]{babel}

\begin{document}
\newpage
The most important inventions.\\

    Good morning everybody.

    Let me start with the question: which inventions do you consider the most significant for humanity? Today I’m going to tell you about the most important inventions from my point of view.

    Because of the limited time, I’ll present you three inventions: electrical engine, transistor and the Internet.

    I’ll be happy to answer your questions at the end of my talk.

    Firstly, let’s take a look at electrical engine.
    Electrical engine is an machine that converts electrical energy into mechanical energy. The first electric motors were simple electrostatic devices described in experiments by Andrew Gordon and Benjamin Franklin in the 1740s. Electrical engines let us distribute energy easily by electricity, and then convert it in mechanical energy.

    Let’s turn now to transistor.
    Transistor is the one of most important part of any electrical circuit. It means that now transistors are literally everywhere. The invention of the transistor was an unexampled development in the electronics industry. It marked the beginning of the current age. After the transistor's invention, advances in technology became more frequent, the most notable of which was computer technology. The three physicists who invented the transistor were awarded with the Nobel Prize.

    And finally, let’s look at the Internet.
    The history of the Internet begins with the development of electronic computers. The Internet has changed the computer and communications world like nothing before. The Internet is the wold wide net, which connects the incredible number of computers. Thanks to it communication and search of some information became much easier.

    Let me summarise what we have looked at.
    Electrical engine let us distribute mechanical energy easily.
    Transistor became a beginning of the age of computers.
    Internet is a good way of communication and search of information.
    That’s all I have to say.

    At last, I hope I have succeeded in presenting to you important inventions.
    Thanks for your attention.
    Are there any questions?
\end{document}